Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-02-08 chapters/ch_results.tex
Pion spectra added

\section{$\pi$ Yields}
Add figure on Glauber model 
Add figure on comparison to FOPI data
Add figure of angular coverage of TPC spectra

@@

>>>>

\section{Pion Spectra and Yields}
Add figure on Glauber model 
Add figure on comparison to FOPI data
Add figure of angular coverage of TPC spectra

@@

\section{Pion Double Ratio}
Add figure of Theory for pion ratios
